Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
added proof Koszul dual

\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}\footnote{As the main objective of~\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon} was a combinatorial model for support $\tau$-tilting complexes of gentle algebras, we did require that the ideal~$I$ was admissible so that~$kQ/I$ was finite dimensional. However, the same proof directly applies in the generality of this paper.}]
The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
\end{theorem}

@@

@@

In this section, we show that the non-kissing complex is a \defn{pseudomanifold},~\ie
\begin{enumerate}[(i)]
\item \defn{pure}: all maximal non-kissing simplices have the same number of walks as~$\dissection$, and
\item \defn{thin}: any codimension~$1$ simplex of~$\NKC$ is contained in exactly two maximal non-kissing simplices.
\end{enumerate}

>>>>

\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
\end{theorem}

@@

\begin{proof}
 The duality gives a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and induces a bijection~$\alpha\in (Q_\dissection)_1\mapsto \alpha\dual\in (Q_{\dissection\dual})_1$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
 Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
\end{proof}

@@

In this section, we show that the non-crossing and non-kissing complexes are \defn{pseudomanifold}, \ie that there are
\begin{enumerate}[(i)]
\item \defn{pure}: all maximal $\dissection$-accordion simplices have the same number of $B$-curves as~$\dissection$, and
\item \defn{thin}: any codimension~$1$ simplex of~$\AC$ is contained in exactly two maximal $\dissection$-accordion simplices.
\end{enumerate}
